Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
slight changes

We evaluated our model, HSLDA, against the comparison models with a focus
on predictive performance. Predictive performance was measured with
standard metrics of performance - sensitiviy (true positive rate) and 
1-specificity (false positive rate). We evaluate on the two aforementioned
datasets to demonstrate that model performance generalizes over two very disparate
domains.

To evaluate the performance of these models, we establish a gold standard for comparison.
In our evaluation of each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against the observed
labeling. Specifically, ancestors of observed nodes were ignored, observed nodes 
were considered positive and unobserved nodes were considered to be negative. This method of 
defining positive and negative labels was chosen to be as fair as possible to all models
being compared.  In particular, since the sLDA model does not enforce the hierarchical
constraints, the models can be compared on a more equal footing by focusing on the observed labels
as positives. The gold standard defined in this way will likely lead to a slight overestimation of the number of
false positives. It is known that ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.

@@

For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
after inference.  However, as intended, they both highlight model performance
under more or less stringent requirements for predicting positive labels.

Figures \ref{fig:main_clinical_results} and \ref{fig:main_amazon_results} show the predictive performance
of HSLDA relative to the three comparison models.

\begin{figure}[htbp]
\begin{center}
%\subfigure[][\label{1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][\label{1b}]{\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%\subfigure[][\label{1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
%\subfigure[][\label{1d}]{\includegraphics[width=.49\textwidth]{figs/one_m_spec_comparison_leafs}}
\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records.  
In all figures, solid is HSLDA, dashed are independent regressors + sLDA (hierarchical 
constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
tree-conditional regressions. \subref{} shows predictive performance as a function of the 
auxiliary variable threshold and \subref{1b} shows predictive perfmance as a function of the
prior mean on regression parameters.}
\label{fig:main_clinical_results}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
%\subfigure[][\label{1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
\subfigure[][\label{1b}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
%\subfigure[][\label{1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
%\subfigure[][\label{1d}]{\includegraphics[width=.49\textwidth]{figs/one_m_spec_comparison_leafs}}
\caption{Out-of-sample Amazon product category predictions from product free-text descriptions.  
In all figures, solid is HSLDA, dashed are independent regressors + sLDA (hierarchical constraints 
on labels ignored), and dotted is HSLDA fit by running LDA first then running tree-conditional 
regressions. \subref{} shows predictive performance as a function of the 
auxiliary variable threshold and \subref{1b} shows predictive perfmance as a function of the
prior mean on regression parameters.}
\label{fig:main_amazon_results}
\end{center}
\end{figure}

>>>>

We evaluated our model, HSLDA, against the comparison models with a focus
on predictive performance. Predictive performance was measured with
standard metrics - sensitiviy (true positive rate) and 
1-specificity (false positive rate). We evaluate on the two aforementioned
datasets to demonstrate that our model generalizes to two different
domains.

To evaluate the performance of these models, we established a gold standard for comparison.
For each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against a standard derived
from the observed labeling. Specifically, ancestors of observed nodes were ignored, observed nodes 
were considered positive and unobserved nodes were considered to be negative. This method of 
defining positive and negative labels was chosen to be as fair as possible to all models
being compared.  In particular, since the sLDA model does not enforce the hierarchical
constraints, the models can be compared on a more equal footing by considering only on the observed labels
as being positive despite the fact that ancestors must also be positive. The gold standard 
defined in this way will likely lead to a slight overestimation of the number of
false positives. It is known that ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives.
However, given that the label space is often large (as in our examples) it is a moderate assumption that
erroneous false positives should not skew results significantly.

@@

For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
following inference.  However, as intended, they both highlight model performance
under more or less stringent requirements for predicting positive labels.

Figure \ref{fig:main_results} shows the predictive performance of HSLDA 
relative to the three comparison models. In figure %\ref{fig:1b}.

%\begin{figure}%[htbp]
%\begin{center}
%%\subfloat[][\label{1a}]{\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
%\subfigure[][]{\label{1b}\includegraphics[width=.49\textwidth]{figs/clin_pred_varying_mu}}
%%\subfloat[][\label{1c}]{\includegraphics[width=.49\textwidth]{figs/sens_comparison_leafs}}
%\subfigure[][]{\label{1d}\includegraphics[width=.49\textwidth]{figs/amazon_pred_varying_mu}}
%\caption{Out-of-sample ICD-9 code prediction from patient free-text discharge records 
%(\subref{} and \subref{1b}). Out-of-sample Amazon product category predictions from 
%product free-text descriptions (\subref{} and \subref{1d}). In all figures, solid is 
%HSLDA, dashed are independent regressors + sLDA (hierarchical 
%constraints on labels ignored), and dotted is HSLDA fit by running LDA first then running 
%tree-conditional regressions. \subref{} and \subref{} show predictive performance as a function of the 
%auxiliary variable threshold and \subref{1b} and \subref{1d} show predictive perfmance as a function of the
%prior mean on regression coefficients.}
%\label{fig:main_results}
%\end{center}
%\end{figure}

%\begin{figure}[t]
%\centering
%\parbox{0.9\columnwidth}{
% \vspace*{-\subfigtopskip}
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.01\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0155626\\
%         \mbox{~~~~~~}LEX: new acute myocardial infarction\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0520887\\
%         \mbox{~~~~~~}LEX: ST-segment depression
%       }}}
% }\goodgap
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.02\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0155626\\
%         \mbox{~~~~~~}LEX: new acute myocardial infarction\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0002962\\
%         \mbox{~~~~~~}LEX: prior angina%
%       }}}
% }\\     \vspace*{-\subfigtopskip}
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.03\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0011065\\
%         \mbox{~~~~~~}LEX: death\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0520887\\
%         \mbox{~~~~~~}LEX: ST-segment depression%
%       }}}
% }\goodgap
% \subfigure[]{
%   \fbox{\parbox{0.35\columnwidth}{\scriptsize
%       \textsf{TEMPLATE Id: 12.04\\
%         FILE No: ahj\_137\_02\_0424\\
%         SENTENCE No: S-98\\
%         RELATION: prediction\\
%         ANALYSIS TYPE: independent\\
%         FINDING(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0011065\\
%         \mbox{~~~~~~}LEX: death\\
%         PARAMETER(S):\\
%         \mbox{~~~}ITEM: \\
%         \mbox{~~~~~~}CUI: C0002962\\
%         \mbox{~~~~~~}LEX: prior angina%
%       }}}
% }}
%\caption{A Content Item after atomization.}\label{fig:org-afteratom}
%\end{figure}
